Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2012-12-06 doc/paper-lcr.tex
finalized draft

\author[Collett \etal]{%
  Thomas~E.~Collett$^{1}$\thanks{\collettemail},
  Philip~J.~Marshall$^{2}$,
  Matthew~W.~Auger$^{1}$,
  Stefan~Hilbert$^{3}$,
\newauthor{%
  Sherry~H.~Suyu$^{4}$,
  Zachary~Greene$^{4}$,
  Tommaso~Treu$^{4}$\thanks{\packard},
  Christopher~D.~Fassnacht$^{5}$,}
\newauthor{%
  L\'eon~V.~E.~Koopmans$^{6}$,
  Maru\v{s}a Brada\v{c}$^{5}$,
  Roger~D.~Blandford$^{3}$} 
  \medskip\\
  $^1$\ioa\\
  $^2$\oxford\\
  $^3$\kipac\\
  $^4$\ucsb\\
  $^5$\davis\\
  $^6$\kapteyn
}

@@

High precision cosmological distance measurements towards individual objects
such as time delay gravitational lenses or type Ia supernovae are affected by
weak lensing perturbations by galaxies and groups along the line of sight. In
time delay gravitational lenses, ``external convergence,'' $\kappax$, can
dominate the uncertainty in the inferred distances. In this paper we attempt
to reconstruct $\kappax$, due to line of sight structure using a simple halo
model.
%
We use mock catalogues from the Millennium Simulation, and calibrate and 
compare our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth
values:  taking into account realistic uncertainties on redshift and stellar
masses, \phil{we find that the reconstruction provides an improvement in
precision of 50\% over the global $\pr(\kappax)$.} 
%
We find that the lowest $\kappax$ lines of sight have the best constrained 
$\pr(\kappax)$. We find that selecting the third of the systems with the
highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
delay distance measurements \phil{with (on average) just} 1\% uncertainty due
to line of sight external convergence effects. Photometric data alone is
sufficient to pre-select the best-constrained lines of sight, and can be done
before investment in lightcurve monitoring. 
%
\phil{Conversely, we show that somehow preferentially selecting lines of sight
with high external shear could, with the reconstruction model presented here,
induce biases of up to 1\% in time delay distance.}  We suggest areas for the
improvement of this general analysis framework (including more sophisticated
treatment of high mass structures) that should allow yet more accurate
cosmological inferences to be made.

@@

\citet{HilbertEtal2009} calculated the lensing convergence using the
``lightcone'' dark matter only  output of the \MS, providing 1.7 degree
square  mock sky maps of this quantity. In this process, the dark matter
density from the simulation was projected onto a set of lens planes at
discrete redshifts, adaptively gridded and smoothed, and then the second
derivatives of the  lensing potential required for the components of the
magnification matrix were computed using a multiple lens plane ray tracing
algorithm. The first order approximation to this algorithm \citep[equation 17
of][]{HilbertEtal2009} gives the total convergence at a given sky
position~$\bmath{\theta}$ as the simple summation of the surface density in
each lens plane, weighted by the inverse critical surface density $\Sigma_{\rm
cr}$ for that plane's redshift:
\be
\kappax(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
                                     {\Sigma_{\rm cr}(z_i,\zs)}.
\ee
\citet{HilbertEtal2009} found this approximation was found to be accurate to a few percent or better
in $\kappax$, even on 30 arcsecond scales.

@@

We require a method for estimating the convergence at any point on the sky,
given a catalogue of observed galaxy properties such as positions,
brightnesses, colours, and possibly stellar masses and redshifts, for every
galaxy in the field of the lens, down to some magnitude limit. Since we cannot
observe the surface mass density of each halo directly, we need some way of
estimating the mass of each halo in the catalogue, so that we can compute its
contribution to the total $\kappax$ along the line of sight \citep[as in
\eg][]{GunnarssonEtal2006,WongEtal2011,KarpenkaEtal2012}.  This mass
assignment recipe will be uncertain, and also incomplete, but it can be
calibrated with cosmological simulations, which represent a significant
additional source of information to what is present in the data.

@@

Many studies have shown that galaxies have total mass density profiles that
are approximately isothermal in their inner regions
\citep[\eg][]{AugerEtal2010} due to the more concentrated stellar mass
component; however, at radii of tens of kpc (tens of arcsec), we expect the
halo density profile to be dark matter dominated, and fall off faster than
$r^{-2}$. This has been confirmed by galaxy-galaxy weak lensing measurements 
\citep[\eg][]{Mandelbaum,Leauthaud}. We note that the two halo term that
dominates the galaxy-galaxy lensing signal at large radii is explicitly taken
into account in our model, where every galaxy is assigned a dark matter halo.

@@

Our halo model accounts for the convergence contribution of density
perturbations that can be associated with light. Filaments and dark
substructures contribute additional convergence, while voids contribute a
divergence; these structures must be included to produce an unbiased estimate
of $\kappax$. In particular, neglecting voids would lead to a heavily biased
estimate of $\kappax$, since the halo model's $\kappah$ can only be positive.
In principle the absence of galaxies implies something about the presence a
void, but we do not currently attempt to use this information. In general, it
is difficult to account for the unseen mass, since we do not have a good model
for its density structure.

@@

This procedure of reducing the full PDF for $\kappah$ to its median increases
the importance of the realism of the simulation: the simulation needs to be a
similar as possible to the real universe or there is a possibility of
systematic errors. Conversely, making use of all the information
in the photometric catalogue yields $\kappax$ estimates of increased
precision.

@@

\Fref{fig:jointkh-k} shows the conditional distribution of $\kappax$ given 
$\kappah$, derived from $10^5$ randomly selected \MS lines of sight
and assuming noise-free halo masses and redshifts. 
\phil{(In this case, $\pr(\kappah|\data)$ is almost delta function since the only uncertainty is halo
concentration, which has minimal effect on $\pr(\kappah|\data)$.  
)}.
% In this case, the PDF : we can read
% off  $\pr(\kappax|\data)$ just by taking a thin vertical slice through this 
% distribution. 
% Note that the joint PDF plotted in this figure is the product
% of  the conditional distribution that we need for calibration, and also the
% prior PDF for $\kappah$ that we need to ensure that the global distribution of
% $\kappah$ values is defaulted to in the case of poor observational data. 
At fixed $\kappah$ we find in \Fref{fig:jointkh-k} that the scatter in 
$\kappax$
grows with $\kappah$; our reconstruction is better at reproducing under-dense
lines of sight than over-dense lines of sight. The effect of ignoring voids
and the smooth mass component is evident in this plot: $\kappah$ is
significantly higher than $\kappax$, at any given $\kappax$ value. 
\phil{Conditioning on $\kappah$ gives a PDF for
$\kappax$ centred at the correct place, by construction.}

@@

We now move on to consider the halo model reconstruction of line of sight mass
distributions given noisy astronomical observables. A typical imaging survey
can be expected to provide measurements of the positions and magnitudes of
galaxies in a field;  spectra for some of the objects may either come from a
synergistic survey, or from targeted follow-up. In this section we quantify
the uncertainties induced by inferring the halo mass and redshift from these
observables.

@@

Given an uncertain stellar mass and redshift it is possible to infer a
halo mass using the stellar mass--halo mass relation of
\citet{BehrooziEtal2010}. This \proceedure requires an inversion of the
relation given in \citet{BehrooziEtal2010} and correctly inverting the
relation's uncertainties requires care: the \proceedure we use to do this
is given in \Aref{appendix:MSMH}. By drawing sample halo masses
and redshifts, we can infer a sample $\kappah$ using the \proceedure of
\Sref{sec:model}; repeatedly drawing samples allows us to
estimate $\pr(\kappah|\data)$ for each reconstructed line of sight. We then
transform this into our target PDF $\pr(\kappax|\data)$ as described above.

@@

While it is good to reconstruct $\kappax$ precisely, it is more important that
$\kappax$ is reconstructed accurately. The reconstruction must not be biased. 
We quantify the accuracy of our reconstructed $\pr(\kappax|\data)$ in the
following way. By shifting the \infered $\pr(\kappax|\data)$ for each line of
sight by the true (ray-traced) convergence, we obtain a  PDF that should be
centred on zero; these offset PDFs can be multiplied together for multiple
lines of sight to emulate a joint likelihood analysis, and then test for
possible bias in it:
\be
\label{eq:bias}
\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true}|\data)
\ee
In this section, we quantify the bias as the size of the deviation in the
expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
is smaller than the half-width of $\mathcal{P}_N$, our $\kappax$ inferences
can be considered accurate. Since the width of $\mathcal{P}_N$ decreases as
more sightlines are combined, a small bias will always 
eventually be found. In the context of measuring time-delay distance at the 
one percent level, the expectation value of $|\mathcal{P}_N|$ needs to be 
significantly less than 0.01. \tom{External convergence is not the only source
of uncertainty in measuring time-delay distance. Since the statistical
distance uncertainties due to lens modelling and time delay estimation are
likely to be at the 3-4\% level \citep{SuyuEtal2010}, convolving
$\mathcal{P}_N$ with a Gaussian of width $0.03/\sqrt{N}$ is a reasonable
approximation for the likely final uncertainty on time-delay distance.}

@@

\phil{We can test the impact of such a shear selection by selecting only lines
of sight with an external shear above some threshold.  We define a somewhat
extreme selection  of $\gammax>0.05$, and find that in this sample, $\kappax$
would be systematically underestimated at the $\sim$0.008 level (corresponding
to a 0.8\% systematic error in distance).}  In the absence of other sources of
uncertainty, this systematic error would be significant in a sample of just 5
lenses;  approximating strong-lens modelling uncertainties as an unbiased
Gaussian with width 4\% on time-delay distance a 0.8\% bias would be
significant for $\sim$20 lenses. \flag{We said 3\% earlier! Can you check for
consistency please? And we only need to explain the Gaussian convolution
once.} This systematic error is mitigated if only the lines of sight with both
$\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are used, but in this
case a bias at the $\sim$0.005 level remains.

While $\gammax>0.05$) is likely to be a much stronger selection than would
occur in reality, it is  nevertheless worth noting from this example  that the
reconstruction \proceedure \phil{can be biased if lens selection functions are
extreme and unaccounted for.} Since our model does not include shear
constraints it is not surprising that a selection function based on shear can
induce a bias. A more sophisticated model that includes the shear recovered
from the lens modelling may be less susceptible to this bias.

The halo model can also be used to estimate the external shear along a line of
sight: shear is an observable that can be extracted from strong lens
modelling. However, there is a degeneracy between internal and external shear.
When the Einstein Ring imaging data are very good it is possible to
disentangle external and internal shear \citep[\eg][]{SuyuEtal2010}, but there
are still significant uncertainties: \citet{WongEtal2011} attempted to match
the shear from strong lens models with a reconstruction of the local lens
group environment, but found a tension between the strong lens model and the
reconstruction of the environment. Given the \citet{WongEtal2011} results, it
is unclear whether the external shear from lens models can be reconciled with
a line of sight reconstruction. Alternatively, it may be possible  to infer
external shear using weak lensing information from near the line of sight.  If
the true external shear can be measured, it provides an additional constraint
on which of the \MS lines of sight are similar to the reconstructed line of
sight. \citet{SuyuEtal2012} found that in the case of 
RXJ1131, combining shear constraints
with galaxy number count over-density gave a significantly different
$\pr(\kappax|\gamma,N_{45})$ compared to the PDF from number count
over-density alone, $\pr(\kappax|N_{45})$.

@@

Clusters, filaments and voids are more difficult to model, but simple forms
could in principle be derived from the structures found in the simulations,
and included in the halo model in some way.  Most importantly for the highest
$\kappax$ lines of sight will be a better group and cluster model:
\citet{MomchevaEtal2006} and  \citet{WongEtal2011} recommend using models
where dark mass is assigned to both galaxy-scale halos and halos for the
groups and clusters they occupy: to make this work, one could incorporate a
group and cluster finder, and then infer halo mass from optical richness
\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass. \tom{Meanwhile,
improving the modelling of voids could be done using suggestions by
\citet{voids2} or \citet{voids1} combined with a void finder such as in
\citet{voids3}. Combining an advanced halo model with a void model will allow
a direct test of the halo approximation: using real photometric data one could
reconstruct lines of sight and compare against measured weak lensing shears.
This would ensure that the reconstruction model reproduces the contents of the
real universe, rather than a particular simulation.}

@@

The reduction of $\pr(\kappah|\data)$ to just its median value, before using
it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
and Greene et al (submitted). The reconstruction method presented here  can be
seen as the limiting case of the weightings explored by Greene et al: rather
than using weighted number counts in an aperture, we treat each galaxy
individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
place. \flag{How much more precise are we than Greene et al?}

>>>>

\author[Collett \etal]{%
  Thomas~E.~Collett$^{1}$\thanks{\collettemail},
  Philip~J.~Marshall$^{2}$,
  Matthew~W.~Auger$^{1}$,
  Stefan~Hilbert$^{3}$,
\newauthor{%
  Sherry~H.~Suyu$^{3,4}$,
  Zachary~Greene$^{4}$,
  Tommaso~Treu$^{4}$\thanks{\packard},
  Christopher~D.~Fassnacht$^{5}$,}
\newauthor{%
  L\'eon~V.~E.~Koopmans$^{6}$,
  Maru\v{s}a Brada\v{c}$^{5}$,
  Roger~D.~Blandford$^{3}$} 
  \medskip\\
  $^1$\ioa\\
  $^2$\oxford\\
  $^3$\kipac\\
  $^4$\ucsb\\
  $^5$\davis\\
  $^6$\kapteyn
}

@@

High precision cosmological distance measurements towards individual objects
such as time delay gravitational lenses or type Ia supernovae are affected by
weak lensing perturbations by galaxies and groups along the line of sight. In
time delay gravitational lenses, ``external convergence,'' $\kappax$, can
dominate the uncertainty in the inferred distances. In this paper we attempt
to reconstruct $\kappax$, due to line of sight structure using a simple halo
model.
%
We use mock catalogues from the Millennium Simulation, and calibrate and 
compare our reconstructed $\pr(\kappax|\data)$ to ray-traced $\kappax$ truth
values:  taking into account realistic uncertainties on redshift and stellar
masses, \tom{we find that the reconstruction of $\kappax$ provides an improvement in
precision of $\sim$50\% over previously published schemes.} 
%
We find that the lowest $\kappax$ lines of sight have the best constrained 
$\pr(\kappax)$. In anticipation of future samples with thousands of lenses,
we find that selecting the third of the systems with the
highest precision $\kappax$ estimates gives a  sub-sample of unbiased time
delay distance measurements \phil{with (on average) just} 1\% uncertainty due
to line of sight external convergence effects. Photometric data alone is
sufficient to pre-select the best-constrained lines of sight, and can be done
before investment in lightcurve monitoring. 
%
\phil{Conversely, we show that somehow selecting lines of sight
with high external shear could, with the reconstruction model presented here,
induce biases of up to 1\% in time delay distance.}  We suggest areas for the
improvement of this general analysis framework (including more sophisticated
treatment of high mass structures) that should allow yet more accurate
cosmological inferences to be made.

@@

\citet{HilbertEtal2009} calculated the lensing convergence using the
``lightcone'' dark matter only  output of the \MS, providing 1.7 degree
square  mock sky maps of this quantity. In this process, the dark matter
density from the simulation was projected onto a set of lens planes at
discrete redshifts, adaptively gridded and smoothed, and then the second
derivatives of the  lensing potential required for the components of the
magnification matrix were computed using a multiple lens plane ray tracing
algorithm. The first order approximation to this algorithm \citep[equation 17
of][]{HilbertEtal2009} gives the total convergence at a given sky
position~$\bmath{\theta}$ as the simple summation of the surface density in
each lens plane, weighted by the inverse critical surface density $\Sigma_{\rm
cr}$ for that plane's redshift:
\be
\kappax(\bmath{\theta}) = \sum_i \frac{\Sigma_i(\bmath{\theta})}
                                     {\Sigma_{\rm cr}(z_i,\zs)}.
\ee
\citet{HilbertEtal2009} found that this approximation is accurate to a few percent or better
in $\kappax$, even on 30 arcsecond scales.

@@

We require a method for estimating the convergence at any point on the sky,
given a catalogue of observed galaxy properties such as positions,
brightnesses, colours, and possibly stellar masses and redshifts, for every
galaxy in the field of the lens, down to some magnitude limit. Since we cannot
observe the surface mass density of each halo directly, we need some way of
estimating the mass of each halo in the catalogue, so that we can compute its
contribution to the total $\kappax$ along the line of sight \citep[as in
\eg][]{GunnarssonEtal2006,KarpenkaEtal2012}.  This mass
assignment recipe will be uncertain, and also incomplete, but it can be
calibrated with cosmological simulations, which represent a significant
additional source of information to what is present in the data.

@@

Many studies have shown that galaxies have total mass density profiles that
are approximately isothermal in their inner regions
\citep[\eg][]{AugerEtal2010} due to the more concentrated stellar mass
component.
This has been confirmed by galaxy-galaxy weak lensing measurements 
\citep[\eg][]{Mandelbaum,Leauthaud}. We note that the two halo term that
dominates the galaxy-galaxy lensing signal at large radii is explicitly taken
into account in our model, where every galaxy is assigned a dark matter halo.
At large radii an NFW-like profile is probably appropriate, but may not be
correct when a halo is very close to the line of sight.

@@

Our halo model accounts for the convergence contribution of density
perturbations that can be associated with light. Filaments and dark
substructures contribute additional convergence, while voids contribute a
divergence; these structures must be included to produce an unbiased estimate
of $\kappax$. In particular, neglecting voids would lead to a heavily biased
estimate of $\kappax$, since the halo model's $\kappah$ can only be positive.
In principle the absence of galaxies implies something about the presence of a
void, but we do not currently attempt to use this information. In general, it
is difficult to account for the unseen mass, since we do not have a good model
for its density structure.

@@

This procedure of reducing the full PDF for $\kappah$ to its median increases
the importance of the realism of the simulation: the simulation needs to be as
similar as possible to the real universe or there is a possibility of
systematic errors. Conversely, making use of all the information
in the photometric catalogue yields $\kappax$ estimates of increased
precision.

@@

\Fref{fig:jointkh-k} shows the conditional distribution of $\kappax$ given 
$\kappah$, derived from $10^5$ randomly selected \MS lines of sight
and assuming noise-free halo masses and redshifts. 
\phil{(In this case, $\pr(\kappah|\data)$ is almost a delta function since the only uncertainty is halo
concentration, which has minimal effect on $\pr(\kappah|\data)$.  
)}.
% In this case, the PDF : we can read
% off  $\pr(\kappax|\data)$ just by taking a thin vertical slice through this 
% distribution. 
% Note that the joint PDF plotted in this figure is the product
% of  the conditional distribution that we need for calibration, and also the
% prior PDF for $\kappah$ that we need to ensure that the global distribution of
% $\kappah$ values is defaulted to in the case of poor observational data. 
At fixed $\kappah$ we find in \Fref{fig:jointkh-k} that the scatter in 
$\kappax$
grows with $\kappah$; our reconstruction is better at reproducing under-dense
lines of sight than over-dense lines of sight. The effect of ignoring voids
and the smooth mass component is evident in this plot: $\kappah$ is
significantly higher than $\kappax$, at any given $\kappax$ value. 
\phil{Conditioning on $\kappah$ gives a PDF for
$\kappax$ centred at the correct place, by construction.}

@@

We now move on to consider the halo model reconstruction of line-of-sight mass
distributions given noisy astronomical observables. A typical imaging survey
can be expected to provide measurements of the positions and magnitudes of
galaxies in a field;  spectra for some of the objects may either come from a
synergistic survey, or from targeted follow-up. In this section we quantify
the uncertainties induced by inferring the halo mass and redshift from these
observables.

@@

Given an uncertain stellar mass and redshift it is possible to infer a
halo mass using the stellar mass--halo mass relation of
\citet{BehrooziEtal2010}. This \proceedure requires an inversion of the
relation given in \citet{BehrooziEtal2010} and correctly inverting the
relation's uncertainties requires care: the \proceedure we use to do this
is given in \Aref{appendix:MSMH}. By drawing sample halo masses
and redshifts, we can infer a sample $\kappah$ using the \proceedure of
\Sref{sec:model}. Repeatedly drawing samples allows us to
estimate $\pr(\kappah|\data)$ for each reconstructed line of sight. We then
transform this into our target PDF $\pr(\kappax|\data)$ as described above.

@@

While it is good to reconstruct $\kappax$ precisely, it is more important that
$\kappax$ is reconstructed accurately. The reconstruction must not be biased. 
We quantify the accuracy of our reconstructed $\pr(\kappax|\data)$ in the
following way. By shifting the \infered $\pr(\kappax|\data)$ for each line of
sight by the true (ray-traced) convergence, we obtain a  PDF that should be
centred on zero; these offset PDFs can be multiplied together for multiple
lines of sight to emulate a joint likelihood analysis, and then test for
possible bias in it:
\be
\label{eq:bias}
\mathcal{P}_N = \prod_{i=1}^N \pr_i(\kappax-\kappax^{\rm true}|\data)
\ee
In this section, we quantify the bias as the size of the deviation in the
expectation value of $\mathcal{P}_N$ from zero. If the bias of $\mathcal{P}_N$
is smaller than the half-width of $\mathcal{P}_N$, our $\kappax$ inferences
can be considered accurate. Since the width of $\mathcal{P}_N$ decreases as
more sightlines are combined, a small bias will always 
eventually be found. In the context of measuring time-delay distance at the 
one percent level, the expectation value of $|\mathcal{P}_N|$ needs to be 
significantly less than 0.01. \tom{External convergence is not the only source
of uncertainty in measuring time-delay distance. Since the statistical
distance uncertainties due to lens modelling and time delay estimation are
likely to be at the 3-4\% level \citep{SuyuEtal2010}, convolving
$\mathcal{P}_N$ with a Gaussian of width $0.04/\sqrt{N}$ is a reasonable
approximation for the likely final uncertainty on time-delay distance.}

@@

\phil{We can test the impact of such a shear selection by selecting only lines
of sight with an external shear above some threshold.  We define a somewhat
extreme selection  of $\gammax>0.05$, and find that in this sample, $\kappax$
would be systematically underestimated at the $\sim$0.008 level (corresponding
to a 0.8\% systematic error in distance).}  In the absence of other sources of
uncertainty, this systematic error would be significant in a sample of just 5
lenses; when including other time-delay distance uncertainties a 0.8\% bias would be
significant for $\sim$20 lenses. This systematic error is mitigated if only the lines of sight with both
$\gammax>0.05$ and well constrained $\pr(\kappax|\data)$ are used, but in this
case a bias at the $\sim$0.005 level remains.

While $\gammax>0.05$ is likely to be a much stronger selection than would
occur in reality, it is  nevertheless worth noting from this example that the
reconstruction \proceedure \phil{can be biased if lens selection functions are
extreme and unaccounted for.} Since our model does not include shear
constraints it is not surprising that a selection function based on shear can
induce a bias. A more sophisticated model that includes the shear recovered
from the lens modelling might be less susceptible to this bias.

The halo model can also be used to estimate the external shear along a line of
sight: shear is an observable that can be extracted from strong lens
modelling. However, there is a degeneracy between internal and external shear.
When the Einstein Ring imaging data are very good it is possible to
disentangle external and internal shear \citep[\eg][]{SuyuEtal2010}, but there
are still significant uncertainties. \citet{WongEtal2011} attempted to match
the shear from strong lens models with a reconstruction of the local lens
group environment, but found a tension between the strong lens model and the
reconstruction of the environment. Given the \citet{WongEtal2011} results, it
is unclear whether the external shear from lens models can be reconciled with
a line-of-sight reconstruction. Alternatively, it may be possible  to infer
external shear using weak lensing information from near the line of sight.  If
the true external shear can be measured, it provides an additional constraint
on which of the \MS lines of sight are similar to the reconstructed line of
sight. \citet{SuyuEtal2012} found that in the case of 
RXJ1131, combining shear constraints
with galaxy number count over-density gave a significantly different
$\pr(\kappax|\gamma,N_{45})$ compared to the PDF from number count
over-density alone, $\pr(\kappax|N_{45})$.

@@

Clusters, filaments and voids are more difficult to model, but simple forms
could in principle be derived from the structures found in the simulations,
and included in the halo model in some way.  Most importantly for the highest
$\kappax$ lines of sight will be a better group and cluster model:
\citet{MomchevaEtal2006} and  \citet{WongEtal2011} recommend using models
where dark mass is assigned to both galaxy-scale halos and halos for the
groups and clusters they occupy. To make this work, one could incorporate a
group and cluster finder, and then infer halo mass from optical richness
\citep[\eg][]{MaxBCG} in tandem with BCG stellar mass. \tom{Meanwhile,
improving the modelling of voids could be done using suggestions by
\citet{voids2} or \citet{voids1} combined with a void finder such as in
\citet{voids3}. Combining an advanced halo model with a void model will allow
a direct test of the halo approximation: using real photometric data one could
reconstruct lines of sight and compare against measured weak lensing shears.
This would ensure that the reconstruction model reproduces the contents of the
real universe, rather than a particular simulation.}

@@

The reduction of $\pr(\kappah|\data)$ to just its median value, before using
it to look up the appropriate $\pr(\kappax)$ from the simulated sightline
ensemble, is reminiscent of the procedure followed by \citet{SuyuEtal2010},
and Greene et al (submitted). The reconstruction method presented here can be
seen as the limiting case of the weightings explored by Greene et al: rather
than using weighted number counts in an aperture, we treat each galaxy
individually, and predict $\kappa_{\rm h,obs}^{\rm med}$ for use in their
place. Given photometry alone, our reconstruction represents a $\sim$50\% improvement of
the precision compared the number counts used in \citet{SuyuEtal2010}. Greene et al.
made important progress for the most over-dense lines of sight; our
reconstructions are $\sim$30\% more precise than those of Greene et al.
